---
title: "Homework 1"
author: "Lai Wei"
date: "2024-07-01"
output: html_document
---

## T1

```{r}



```

## T2
### a
the output of `max(vector1)`: "7"  
the output of `sort(vector1)`: "12" "32" "5"  "7"  
the output of `sum(vector1)`: Error  
(Reason: The elements in the vector are not values but text, which cannot be added.)

### b
#### b1

the output: Error  
(Reason: When you mix strings and numbers in a vector, all elements of the vector are forcibly converted to character types.)

#### b2

the output: 19

#### b3

the output of `list4[[2]]+list4[[4]]`: 168  
the output of `list4[2]+list4[4]`: Error  
(Reason: It tries to add two sublists, which is not allowed.)

## T3
### a

```{r}
seq(from=1,to=10000,by=372)
seq(from=1,to=10000,length.out=50)
```

### b

Difference: `rep(1:3, times=3)` will repeat the whole vector for 3 times, whose output could be `1 2 3 1 2 3 1 2 3`. However, `rep(1:3, each=3)` will repeat each element of the vector for 3 times, whose output could be `1 1 1 2 2 2 3 3 3`.






