---
title: "Homework 1"
author: "Lai Wei"
date: "2024-07-01"
output: html_document
---

## T1

```{r}
iowa.df<-read.csv("../data/iowa.csv",sep=';',header=T)
iowa.df

length(iowa.df$Year)
length(iowa.df)

names(iowa.df)

iowa.df[[5,7]]

iowa.df[2,]
```

## T2
### a
the output of `max(vector1)`: "7"  
the output of `sort(vector1)`: "12" "32" "5"  "7"  
the output of `sum(vector1)`: Error  
(Reason: The elements in the vector are not values but text, which cannot be added.)

### b
#### b1

the output: Error  
(Reason: When you mix strings and numbers in a vector, all elements of the vector are forcibly converted to character types.)

#### b2

the output: 19

#### b3

the output of `list4[[2]]+list4[[4]]`: 168  
the output of `list4[2]+list4[4]`: Error  
(Reason: It tries to add two sublists, which is not allowed.)

## T3
### a

```{r}
seq(from=1,to=10000,by=372)
seq(from=1,to=10000,length.out=50)
```

### b

Difference: `rep(1:3, times=3)` will repeat the whole vector for 3 times, whose output could be `1 2 3 1 2 3 1 2 3`. However, `rep(1:3, each=3)` will repeat each element of the vector for 3 times, whose output could be `1 1 1 2 2 2 3 3 3`.

## MB.Ch1.2.

```{r}
library(DAAG)
library(ggplot2)

pre_included.df<-orings[c(1,2,4,11,13,18),]

ggplot(pre_included.df,aes(x = Temperature,y = Total))+geom_point()+labs(x = "Temperature",y = "Total")

ggplot(orings,aes(x = Temperature,y = Total))+geom_point()+labs(x = "Temperature",y = "Total")
```

## MB.Ch1.4.

```{r}
library(DAAG)

str(ais)
apply(ais, 2, anyNA)

sex_sport_tb <- table(ais$sex,ais$sport)
sex_sport_tb
(as.vector(sex_sport_tb[1,])/as.vector(sex_sport_tb[2,])) < (1/3) | (as.vector(sex_sport_tb[1,])/as.vector(sex_sport_tb[2,])) > 3
```

## MB.Ch1.6.

```{r}
Manitoba.lakes <- data.frame("elevation" = c(217,254,248,254,253,227,178,207,217), "area" = c(24387,5374,4624,2247,1353,1223,1151,755,657))
row.names(Manitoba.lakes) <- c("Winnipeg","Winnipegosis","Manitoba","SouthernIndian","Cedar","Island","Gods","Cross","Playgreen")
Manitoba.lakes

attach(Manitoba.lakes)
plot(log2(area) ~ elevation, pch=16, xlim=c(170,280))
text(log2(area) ~ elevation, labels=row.names(Manitoba.lakes), pos=4)
text(log2(area) ~ elevation, labels=area, pos=2)
title("Manitoba's Largest Lakes")

plot(area ~ elevation, pch=16, xlim=c(170,280), ylog=T)
text(area ~ elevation, labels=row.names(Manitoba.lakes), pos=4, ylog=T)
text(area ~ elevation, labels=area, pos=2, ylog=T)
title("Manitoba's Largest Lakes")
```

## MB.Ch1.7.

```{r}
library(DAAG)

combined_labels <- paste(rownames(Manitoba.lakes),Manitoba.lakes$area,sep = ":")
dotchart(Manitoba.lakes$area, labels = combined_labels)

combined_labels_log <- paste(rownames(Manitoba.lakes),log2(Manitoba.lakes$area),sep = ":")
dotchart(log2(Manitoba.lakes$area), labels = combined_labels_log)
```

## MB.Ch1.8.

```{r}
library(DAAG)

sum(Manitoba.lakes$area)
```





