---
title: "Solutions for Final2024"
author: "Lai Wei"
date: "2024-07-08"
output: html_document
---
```{r}
library(tidyverse)
```

## 1.

```{r}
A <- matrix(c(9, 5, 2, 9, 4, 0, 6, 2, 12, 7, 8, 9, 2, 9, 0, 11), nrow = 4)
b <- c(7, 18, 1, 0)
solution <- solve(A, b)
solution
```

## 2.

```{r}
xVec <- sample(0:999, 250, replace = TRUE)
yVec <- sample(0:999, 250, replace = TRUE)
```

### a. Create the vector
```{r}
zVec <- yVec[seq(2, 250, by = 2)] - xVec[seq(1, 249, by = 2)]
zVec
```

### b. Pick out the values in yVec which are > 600
```{r}
yVec_greater_than_600 <- yVec[yVec > 600]
yVec_greater_than_600
```

### c. Index positions in yVec of the values which are > 600
```{r}
index_positions <- which(yVec > 600)
index_positions
```

### d. Sort the numbers in xVec in the order of increasing values in yVec
```{r}
sorted_xVec <- xVec[order(yVec)]
sorted_xVec
```

### e. Elements in yVec at index positions 1, 4, 7, ...
```{r}
selected_elements <- yVec[seq(1, length(yVec), by = 3)]
selected_elements
```

## 3.

```{r}
data(state)
state.x77 <- as_tibble(state.x77, rownames = "State")
```

### a. Select states with income < 4300 and calculate average income
```{r}
states_low_income <- state.x77 %>% filter(Income < 4300)
average_income <- mean(states_low_income$Income)
average_income
```

### b. Sort by income and select the state with the highest income
```{r}
state_highest_income <- state.x77 %>% arrange(desc(Income)) %>% slice(1)
state_highest_income
```

### c. Add a variable categorizing the size of population
```{r}
state.x77 <- state.x77 %>%
  mutate(Population_Size = ifelse(Income <= 4500, "S", "L"))
```

### d. Average income and illiteracy by population size
```{r}
average_values <- state.x77 %>%
  group_by(Population_Size) %>%
  summarise(
    avg_income = mean(Income),
    avg_illiteracy = mean(Illiteracy)
  )
average_values
```

## 4.

### a. Function to simulate n observations from uniform distribution
```{r}
simulate_uniform <- function(n) {
  x <- runif(n, 0, 1)
  y <- runif(n, 0, 1)
  tibble(x = x, y = y)
}
```

### b. Function to calculate proportions
```{r}
calculate_proportions <- function(data) {
  dist_to_edge <- pmin(data$x, 1 - data$x, data$y, 1 - data$y)
  dist_to_vertex <- pmin(
    sqrt(data$x^2 + data$y^2),
    sqrt((1 - data$x)^2 + data$y^2),
    sqrt(data$x^2 + (1 - data$y)^2),
    sqrt((1 - data$x)^2 + (1 - data$y)^2)
  )
  prop_edge <- mean(dist_to_edge < 0.25)
  prop_vertex <- mean(dist_to_vertex < 0.25)
  list(prop_edge = prop_edge, prop_vertex = prop_vertex)
}

# Test with n = 1000
set.seed(37)
data <- simulate_uniform(1000)
calculate_proportions(data)
```

## 5.

```{r}
n <- 10000
set.seed(1)
points <- tibble(x = runif(n), y = runif(n))
points <- points %>%
  mutate(inside = map2_dbl(.x = x, .y = y, ~ifelse(.x^2 + .y^2 < 1, 1, 0))) %>%
  rowid_to_column("N")
```

### a. Compute the estimation of π at each row
```{r}
points <- points %>%
  mutate(pi_estimate = 4 * cumsum(inside) / N)
```

### b. Plot the estimates of π against N
```{r}
ggplot(points, aes(x = N, y = pi_estimate)) +
  geom_line() +
  labs(title = "Estimation of π over iterations", x = "N", y = "π Estimate")
```

## 6.

```{r}
suicrates <- tibble(
  Country = c('Canada', 'Israel', 'Japan', 'Austria', 'France', 'Germany', 'Hungary', 'Italy', 'Netherlands', 'Poland', 'Spain', 'Sweden', 'Switzerland', 'UK', 'USA'),
  Age25.34 = c(22, 9, 22, 29, 16, 28, 48, 7, 8, 26, 4, 28, 22, 10, 20),
  Age35.44 = c(27, 19, 19, 40, 25, 35, 65, 8, 11, 29, 7, 41, 34, 13, 22),
  Age45.54 = c(31, 10, 21, 52, 36, 41, 84, 11, 18, 36, 10, 46, 41, 15, 28),
  Age55.64 = c(34, 14, 31, 53, 47, 49, 81, 18, 20, 32, 16, 51, 50, 17, 33),
  Age65.74 = c(24, 27, 49, 69, 56, 52, 107, 27, 28, 28, 22, 35, 51, 22, 37)
)
```

### a. Transform suicrates into long form
```{r}
suicrates_long <- suicrates %>%
  pivot_longer(cols = starts_with("Age"), names_to = "AgeGroup", values_to = "Rate")
```

### b. Construct side-by-side box plots
```{r}
ggplot(suicrates_long, aes(x = AgeGroup, y = Rate)) +
  geom_boxplot() +
  labs(title = "Suicide Rates by Age Group", x = "Age Group", y = "Rate per 100,000")
```
<font size=4.5>*The suicide rate in the age range from 25.34 to 65.74 increases with age, and the difference in suicide rates in different countries increases with age.*</font>

## 7.

```{r}
LaborSupply <- read_csv("LaborSupply.csv")

# Create hour and wage variables
labor <- LaborSupply %>%
  mutate(hour = exp(lnhr), wage = exp(lnwg), .before = kids) %>%
  dplyr::select(-lnhr, -lnwg)
```

### a. Compute average annual hours worked and their standard deviations by year
```{r}
avg_hours_sd <- labor %>%
  group_by(year) %>%
  summarise(
    avg_hours = mean(hour),
    sd_hours = sd(hour)
  )
avg_hours_sd
```

### b. Age group that worked the most hours in 1982
```{r}
most_hours_1982 <- labor %>%
  filter(year == 1982) %>%
  group_by(age) %>%
  summarise(avg_hours = mean(hour)) %>%
  arrange(desc(avg_hours)) %>%
  slice(1)
most_hours_1982
```

### c. Create n_years variable
```{r}
labor <- labor %>%
  group_by(id) %>%
  mutate(n_years = n_distinct(year)) %>%
  ungroup()

# Is the panel balanced?
is_balanced <- all(labor %>% count(id) %>% pull(n) == labor$n_years)
is_balanced
```

### d. Individuals without any kids during the whole period
```{r}
labor <- labor %>%
  group_by(id) %>%
  mutate(no_kids = ifelse(all(kids == 0), 1, 0)) %>%
  ungroup()
```

### e. Average wage, standard deviation, and number of observations for no kids vs kids in 1980
```{r}
stats_1980 <- labor %>%
  filter(year == 1980) %>%
  group_by(no_kids) %>%
  summarise(
    avg_wage = mean(wage),
    sd_wage = sd(wage),
    n = n()
  )
stats_1980
```

